%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[zh,color,11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xeCJK}
\setmonofont{Courier New}
\setCJKmainfont{SimSun}
\setCJKsansfont{KaiTi}
\setCJKmonofont{SimHei}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Yao} % Your first name
\familyname{Dahai} % Your last name

% All information in this block is optional, comment out any lines you don't need
\mobile{(+86) 152-1072-4792}
\email{acprimer.yao@gmail.com}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
\quote{(+86) 152-1072-4792 \quad $\bullet$ \quad acprimer.yao@gmail.com\\https://github.com/acprimer}
\homepage{https://github.com/acprimer}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Job Objective \quad--\quad Software Engineer Intern}

\section{Education}

\cventry{2013--2016}{Beihang University}{Beijing}{\quad Masters of Computer Science}{}{Graduate students first-class scholarship}  
\cventry{2009--2013}{North China Electric Power University}{Beijing}{Bachelor of Computer Science}{top 10\%}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%------------------------------------------------


	
\section{Experience}


\cventry{2014.4--now}{Android development}{ACT, Beihang University}{Beijing}{}{Develop an Android app in the project of iCrowd@Beihang -- subprogram of National Basic Research Program (973 Program).
	\newline{}Project homepage: http://www.service4all.org.cn/iCrowd/
	\newline{}
	Detailed achievements:
	\begin{itemize}
		\item Conduct market research and demand analysis in Beihang University with the help of several students.
		\item Design and implement APIs with JSP servlet.
		\item Design and implement an Android app -- iCrowd with basic functions.
		\item Product user experience research and iterative develop our app to enhance user experience.
	\end{itemize}}
	
\cventry{2014.3--4}{Website development}{ACT, Beihang University}{Beijing}{}{Develop a website of commodity evaluation system. This system targets to accurate analyzing commodity reviews with the help of crowdsourcing.
	\newline{}Project homepage: http://www.service4all.org.cn/crowdsourcing/ratings/
	\newline{}
	Detailed achievements:
	\begin{itemize}
		\item Design and implement the database using MySQL.
		\item Design and implement the website using JSP.
	\end{itemize}}
	

\cventry{2013.3--9}{Android development intern}
{Ruiwuxingzhi Corporation}{Beijing}{}{During my internship, I took part in the company's core project--3GO(an Android app to gather GPRS or 3G flow by doing some tasks.) from start to finish. During that time, I have learned a lot of knowledge of Android development. In addition, I have accumulated rich experience in Android app development process for my future career.
	\newline{}Project homepage: http://3go.3gjiayou.com/
	\newline{}
	Detailed achievements:
	\begin{itemize}
	\item Create prototypes of 3GO Android app using Axure.
	\item Design and implement these modules: Recommendation module, account management module and so on.
	\item Design and implement a application embedded game -- Guess Poetry independently.
	\end{itemize}}
%------------------------------------------------


\section{Research}

\subsection{The Institute of Advanced Computing Technology (ACT), Beihang University}

\cvitem{Project}{Develop an Android app in the project of iCrowd@Beihang -- subprogram of National Basic Research Program (973 Program) }
\cvitem{Research}{Research on Android platform and application secrity}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
\cvitem{2014}{1st prize in the OW2 programming contest, our project is iCrowd@Beihang}
\cvitem{2014}{1st class scholarship, School of Computer Science, Beihang University}
\cvitem{2012}{Silver Medal of \textsc{ACM/ICPC} (International Collegiate Programming Contest) in the Asia regional contest}
\cvitem{2012}{Meritorious Winner of  \textsc{MCM} (Mathematical Contest in Modeling)}
\cvitem{2011-2012}{obtained the National Scholarship twice}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{English Skills}

\cvitem{Basic}{CET 6(542)}
\cvitem{Advanced}{Have a good command of reading English papers and technical documents.}

\section{Computer Skills}

\cvitem{Basic}{Proficient in \textsc{java/C}, familiar with frequently-used data structures and algorithms.}
\cvitem{}{Familiar with\textsc{Jsp} and \textsc{MySQL}.}
\cvitem{Experience}{Skilled in \textsc{Android} development, one year of Android experience.}
\cvitem{}{Website development experience with \textsc{Jsp}, familiar with \textsc{Struts/Hibernate} frameworks.}


\section{Self Evaluation}
\cvitem{}{Solid programming foundation, familiar with algorithms, two years ACM/ICPC contest experience.}
\cvitem{}{Good self-learning ability, solid Math and Logic foundation, receptive to learn new knowledge.}
\cvitem{}{Have a passion for technology, good problem-solving ability, good communication capability.}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block
%----------------------------------------------------------------------------------------

\end{document}